\huge \systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-07-09 poster.tex
affiliation
turtle graphics

\title{\systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning} % Poster title

@@

\institute{Massachusetts Institute of Technology} % Institution(s)

@@

\begin{block}{Ongoing work: Generative models}
  Learn probabilistic program (a regex) $p_n$ from $K$ strings $x_n = \left\{y_n^k \right\}_{k = 1}^K$.

>>>>

\title{\huge \systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning} % Poster title

@@

\institute{Massachusetts Institute of Technology \& MIT-IBM Watson AI lab} % Institution(s)

@@

\begin{block}{Turtle/LOGO Graphics}

  \newcommand{\dreamSize}{5.5cm}
  \begin{tabular}{|lll|}\multicolumn{3}{c}{\textbf{9 (of 132) Tasks}}\\\hline
    \includegraphics[width = \dreamSize]{turtleTasks/square/trimmed/train_square_3_h.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/square/trimmed/train_square_4_h.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/six/trimmed/snow1_h.png}\\
    \includegraphics[width = \dreamSize]{turtleTasks/six/trimmed/snow2_random_1.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/six/trimmed/hexa_vh.png}&
        \includegraphics[width = \dreamSize]{turtleTasks/logoTasks/trimmed/star_5_h.png}\\
%    \includegraphics[width = \dreamSize]{turtleTasks/circle/trimmed/train_circle_10_h.png}\\
    \includegraphics[width = \dreamSize]{turtleTasks/logoTasks/trimmed/smooth_spiral4_h.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/los/trimmed/train_los_3_1_h.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/logoTasks/trimmed/iter2_h.png}\\\hline
%    \includegraphics[width = \dreamSize]{dreams/final/trimmed/1748505267_norm.png}&
  \end{tabular}\hspace{4cm}%
  \begin{tabular}{|lll|}\multicolumn{3}{c}{\textbf{9 samples from learned DSL}}\\\hline
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/4361002260.png}&
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/5809723215.png}&
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/5818934795_norm.png}\\
%    \includegraphics[width = \dreamSize]{dreams/final/trimmed/6027771181.png}\\
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/1950268419.png}&
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/6770710484.png}&
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/7045328293.png}\\
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/7623700519.png}&
%    \includegraphics[width = \dreamSize]{dreams/final/trimmed/8879622788.png}&
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/9150025422.png}&
    \includegraphics[width = \dreamSize]{dreams/final/trimmed/9666602433.png}\\\hline
%    \includegraphics[width = \dreamSize]{dreams/final/trimmed/1748505267_norm.png}&
    \end{tabular}
  Learn probabilistic program (a regex) $p_n$ from $K$ strings $x_n = \left\{y_n^k \right\}_{k = 1}^K$.
